---
title: "An introduction to `svycoxme`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{svycoxme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
This document provides an introduction to `svycoxme`. This package allows users to fit mixed-effect proportional hazards models to data from complex samples. The main function, `svycoxme`, is similar spirit to `survey::svycoxph`. That is, point estimation is handled internally by `coxme::coxme`, which is passed the relevant parameters from the survey design. Extra steps are then taken for variance estimation, which is either by Taylor linearisation or replicate weighting.


# Data generation
Time-to-event data can be generated using the functions `one_dataset` and `draw_event_times`. The first of these functions, `one_dataset`, takes a one-sided formula, plus information about the terms in the equation to generate a dataset with a column of event times.

```{r setup, message=FALSE, warning=FALSE}
library(svycoxme)
```

For example, 

put in example from chapter 2. 

This is the sort of data generation from ripatti palmgren.


```{r one_dataset_example, message=FALSE, warning=FALSE}



```



Example and intent with draw event times




show svycoxme functionality, along with some sampling stuff and calibration



talk about the residuals function






